\subsection{Questionnaire Experiment Group}
\label{app:questionnaire-experiment}
\begin{enumerate}
    \item How efficient would you say you were in following the recipe? (On a scale from 1-10, where 1 = very inefficient, 10 = maximum efficiency)
    
    \item How confident were you about the quantities of each ingredient, given the recipe instructions? (On a scale from 1-10, where 1 = Not at all confident, 10 = Extremely confident)
    
    \item To what extent did you find this way of following the recipe intuitive? (On a scale from 1-10, where 1 = Not intuitive at all, 10 = Very intuitive)
    
    \item Rank which device or medium you use when you use recipes while cooking. (On a scale from 1-4, where 1 = mostly used, 4 = least used)\\
    Phone \hfill Computer \hfill iPad \hfill Paper/Book
    
    \item How would you rate the taste of the dish? (On a scale from 1-10, where 1 = Horrible, 10 = Excellent)
    
    \item How difficult was following the recipe exactly? (On a scale from 1-10, where 1 = Very Difficult, 10 = Very easy)
    
    \item How familiar are you with this recipe? (On a scale from 1-10, where 1 = Completely unfamiliar, 10 = Extremely familiar)
    
    \item To what extent did you feel that the interaction was smooth? (On a scale from 1-10, where 1 = Not smooth at all, 10 = Extremely smooth)
    
    \item Which step would you say was the hardest for you? (Please choose one)\\
    \begin{itemize}
        \item[$\square$] Step 1
        \item[$\square$] Step 2
        \item[$\square$] Step 3
        \item[$\square$] Step 4
        \item[$\square$] Step 5
    \end{itemize}
    
    \item Which step would you say was the easiest for you? (Please choose one)\\
    \begin{itemize}
        \item[$\square$] Step 1
        \item[$\square$] Step 2
        \item[$\square$] Step 3
        \item[$\square$] Step 4
        \item[$\square$] Step 5
    \end{itemize}
    
    \item Did you use the helping circle in the step with the tomato? (Please select Yes or No)\\
    \begin{itemize}
        \item[$\square$] Yes
        \item[$\square$] No
    \end{itemize}
    
    \item Did you use the helping circle in the step with the avocado? (Please select Yes or No)\\
    \begin{itemize}
        \item[$\square$] Yes
        \item[$\square$] No
    \end{itemize}
    
    \item Did you use the helping circle in the step with the onion? (Please select Yes or No)\\
    \begin{itemize}
        \item[$\square$] Yes
        \item[$\square$] No
    \end{itemize}
    
    \item What do you feel would be a good feature to add? (Please specify)
    
    \item Is there anything else in this questionnaire that you would like to comment on, which I forgot to ask about? (Please specify)
    
    \item Did you agree for me to use your video to process it for an experiment? (Please select Yes or No)\\
    \begin{itemize}
        \item[$\square$] Yes
        \item[$\square$] No
    \end{itemize}
\end{enumerate}
