\subsection{Questionnaire Validation Group}
\label{app:questionnaire-validation}
\begin{enumerate}
    \item Select which describes you the most (On a scale from 1-10, where 1 = I was relying on my cooking experience to measure the quantities, 10 = I was focused on getting every gram right)
    
    \item Rate your familiarity with cooking in general (On a scale from 1-10, where 1 = I usually buy made food, or someone cooks for me, 10 = I could make any recipe come to life)
    
    \item How much do you follow recipes when you use them? (On a scale from 1-10, where 1 = I usually just check recipes for the ingredients and then improvise, 10 = I follow every single step and detail described in the recipe)
    
    \item Rate yourself as described below (On a scale from 1-10, where 1 = I never use recipes, 10 = I always use recipes)
    
    \item How familiar are you with this recipe? (On a scale from 1-10, where 1 = I have never eaten or heard of guacamole, 10 = I make guacamole regularly)
    
    \item How efficient would you say you were in following the recipe? (On a scale from 1-10, where 1 = very inefficient, 10 = maximum efficiency)
    
    \item How confident were you about the quantities of each ingredient, given the recipe instructions? (On a scale from 1-10, where 1 = Not at all confident, 10 = Extremely confident)
    
    \item To what extent did you find this way of following the recipe intuitive? (On a scale from 1-10, where 1 = Not intuitive at all, 10 = Very intuitive)
    
    \item Rank which device or medium you use when you use recipes while cooking. (On a scale from 1-4, where 1 = mostly used, 4 = least used)\\
    Phone \hfill Computer \hfill iPad \hfill Paper/Book
    
    \item How would you rate the taste of the dish? (On a scale from 1-10, where 1 = Horrible, 10 = Excellent)
    
    \item How difficult was following the recipe exactly? (On a scale from 1-10, where 1 = Very Difficult, 10 = Very easy)
    
    \item How familiar are you with this recipe? (On a scale from 1-10, where 1 = Completely unfamiliar, 10 = Extremely familiar)
    
    \item To what extent did you feel that the interaction was smooth? (On a scale from 1-10, where 1 = Not smooth at all, 10 = Extremely smooth)
    
    \item Which step would you say was the hardest for you? (Please choose one)\\
    \begin{itemize}
        \item[$\square$] Step 1
        \item[$\square$] Step 2
        \item[$\square$] Step 3
        \item[$\square$] Step 4
        \item[$\square$] Step 5
    \end{itemize}
    
    \item Which step would you say was the easiest for you? (Please choose one)\\
    \begin{itemize}
        \item[$\square$] Step 1
        \item[$\square$] Step 2
        \item[$\square$] Step 3
        \item[$\square$] Step 4
        \item[$\square$] Step 5
    \end{itemize}
    
    \item Did you use the helping circle in the step with the tomato? (Please select Yes or No)\\
    \begin{itemize}
        \item[$\square$] Yes
        \item[$\square$] No
    \end{itemize}
    
    \item Did you use the helping circle in the step with the avocado? (Please select Yes or No)\\
    \begin{itemize}
        \item[$\square$] Yes
        \item[$\square$] No
    \end{itemize}
    
    \item Did you use the helping circle in the step with the onion? (Please select Yes or No)\\
    \begin{itemize}
        \item[$\square$] Yes
        \item[$\square$] No
    \end{itemize}
    
    \item What do you feel would be a good feature to add? (Please specify)
    
    \item Is there anything else in this questionnaire that you would like to comment on, which I forgot to ask about? (Please specify)
    
    \item Did you agree for me to use your video to process it for an experiment? (Please select Yes or No)\\
    \begin{itemize}
        \item[$\square$] Yes
    \end{itemize}
\end{enumerate}